### 2020-08-11 thesis/chap_2.tex
capitalize title

% !TEX root = ./thesis.tex
\chapter{Integrating stakeholders perceptions of connectivity conservation priorities into a spatially explicit land use and connectivity change model}
\begin{center}
{Valentin Lucet$^{1}$, Andrew Gonzalez$^{1}$}\\
\end{center}
\textit{Author Affiliations:}\\
\normalsize{$^{1}$Department of Biology, McGill University}\\

>>>>

% !TEX root = ./thesis.tex
\chapter{Integrating Stakeholders Perceptions of Connectivity Conservation Priorities into a Spatially Explicit Land Use and Connectivity Change Model}
\begin{center}
{Valentin Lucet$^{1}$, Andrew Gonzalez$^{1}$}\\
\end{center}
\textit{Author Affiliations:}\\
\normalsize{$^{1}$Department of Biology, McGill University}\\
